```{r}
#| label: setup
#| include: false
# load datasets and results objects
# place chunk before the yaml header, so sample sizes can be reported in the abstract
library(papaja)
library(flextable)
library(tidyverse)
library(foreign)
dat_poly <- read.spss("data/Haupterhebung Studie III (Polytom 6PS).sav", 
  to.data.frame = TRUE, use.value.labels = FALSE, na.omit = FALSE)
dat_dich <- read.spss("data/Haupterhebung Studie III (Dichotom 2PS).sav",
  to.data.frame = TRUE, use.value.labels = FALSE, na.omit = FALSE)
dat_desc <- bind_rows(
  dat_poly |> select(Geschlecht, Bildung, Muttersprache, Alter_realW) |> mutate(categories = "6 categories"),
  dat_dich |> select(Geschlecht, Bildung, Muttersprache, Alter_realW) |> mutate(categories = "2 categories"))
dat_interviews <- read.spss("data/Stichprobe kognitive Interviews.sav", 
  to.data.frame = TRUE, use.value.labels = FALSE, na.omit = FALSE)
dat_pilot <- read.spss("data/Pilottest_Studie_3.sav", 
  to.data.frame = TRUE, use.value.labels = FALSE, na.omit = FALSE)

results <- readRDS("results/results.rds")
results_secondary <- readRDS("results/results_secondary.rds")

papaja::r_refs(file = "r-references.bib")
```

---
title: "Evaluating Psychological Scales with Gold-Standard Items: Lessons from Measures of Body Height, Weight, and Age"
shorttitle: "Evaluating Scales with Gold-Standard Items"
date: 2025-07-18
date-modified: 2026-04-15
date-format: iso
author:
  - name: Kathryn Eichhorn
    orcid: 0000-0003-3676-9420
    role: 
      - conceptualization
      - investigation
      - resources
      - data curation
      - writing
    affiliations:
      - name: University of the Bundeswehr Munich
        department: Institute of Psychology
        city: Neubiberg
        country: Germany
  - name: Markus Bühner
    corresponding: true
    email: buehner@lmu.de
    orcid: 0000-0002-0597-8708
    role: 
      - formal analysis
      - supervision
      - writing
    affiliations:
      - id: "lmu"
        name: LMU Munich
        department: Department of Psychology
        address: Leopoldstr. 13
        city: D-80802 Munich
        country: Germany
        postal-code: 80802
  - name: Florian Pargent
    orcid: 0000-0002-2388-553X
    role:
      - formal analysis
      - software
      - validation
      - writing
    affiliations:
      - ref: lmu
  - name: Janika Saretzki
    orcid: 0000-0002-6536-8266
    role:
      - editing
    affiliations:
      - name: University of Graz
        department: Department of Psychology
        city: Graz
        country: Austria
      - name: Charlotte Fresenius University of Psychology
        city: Munich
        country: Germany
      - ref: lmu
  - name: Larissa Sust
    orcid: 0000-0002-3389-1626
    role:
      - editing
    affiliations:
      - ref: lmu
  - name: Jonas Hauck
    orcid: 0009-0002-8872-0530
    role:
      - editing
    affiliations:
      - id: "regen"
        name: University of Regensburg
        department: Faculty of Human Sciences
        city: Regensburg
        country: Germany
  - name: Sven Hilbert
    orcid: 0000-0001-5808-8357
    role:
      - conceptualization
      - supervision
      - editing
    affiliations:
      - ref: regen
    
author-note:
  disclosures:
    data-sharing: This is version 3 (last modification {{< meta date-modified >}}) of our preprint published on PsyArXiv at <https://doi.org/10.31234/osf.io/r259d_v2>. All materials (reproducible manuscript, analysis code, datasets, codebooks, questionnaires) are available in the project's repository on the Open Science Framework (OSF) at <https://osf.io/p7492/>. A Quarto Manuscript website is hosted at <https://florianpargent.github.io/gold-standard-items/>. The data have previously been analyzed in the dissertation thesis of the first author at <https://doi.org/10.5282/edoc.23628>. As part of the dissertation, a preregistration was published at <https://osf.io/cz3uv/?view_only=9cac02db231b48629fea9ae53c3038b9> that differs from the analyses reported in the current manuscript.
    conflict-of-interest: The authors declare that they have no financial conflicts of interest in relation to the content of the article and have no non-financial conflicts of interest.
    financial-support: ~
    gratitude: ~
    authorship-agreements: ~
language:
  title-block-role-introduction: "Kathryn Eichhorn and Markus Bühner contributed equally to this manuscript. Author roles were classified using the Contributor Role Taxonomy (CRediT; <https://credit.niso.org/>):"
abstract: "This article investigates whether gold-standard items are helpful for questionnaire development. Based on an initial item pool (138 items) derived through a deductive item construction ($N$ = 124) and prototype approach ($N$ = 24), followed by cognitive interviews ($N$ = `r nrow(dat_interviews)`) and a pilot study ($N$ = `r nrow(dat_pilot)`) of a preliminary item set (61 items), three 12-item scales were constructed to measure the physical traits of body height, body weight, and age. We collected data on these scales using response formats with either two ($N$ = `r nrow(dat_dich)`) or six ($N$ = `r nrow(dat_poly)`) categories. We also collected numeric self-reports of body weight, body height, and age as gold-standard items. We argue that the items intended to measure the latent variable (i.e., body height, body weight, age) most directly (i.e., the gold-standard items) should have the highest loadings on that variable. Contrary to this assumption, confirmatory factor analyses revealed that the gold-standard items did not consistently exhibit the highest loadings on their corresponding latent variables, calling into question the content validity of our scales. Furthermore, when controlling for the self-reported physical body height, body weight, and age as gold-standard items, as well as gender, we did not always find an interpretable, systematic residual variance. Finally, the pattern of correlations among the latent variables did not closely reflect those among the self-reported gold-standard items, suggesting that the item scales and the gold-standard items do not share the same validity. While these results are consistent with previous studies, our analyses also showed that items with two response categories were at least as valid as those with six categories, contradicting past recommendations. Our analyses underscore the importance of intensive cognitive pretesting in scale construction and suggest that questionnaires using different response formats should be compared empirically and that hypotheses about which items best represent the latent variable should be tested."
keywords: [confirmatory factor analysis, content validity, item responses, latent variables, questionnaire development]
license: CC BY 4.0
bibliography: [references.bib, r-references.bib]
floatsintext: true
numbered-lines: false
csl: apa.csl
---

\

::: {.content-visible when-format="html"}
# Introduction
:::

Psychological researchers spend a lot of time developing questionnaires, called psychological scales, and use latent variable modeling to test whether their scales measure the intended psychological construct [@tenholtScaleConstructionEvaluation2010].
When constructing items for a new scale, the common approach is to first carefully define the construct or latent variable to be measured, and then generate indicators for it based on this definition [see @anastasiPsychologicalTests1997].
When based on common factor analytic test models in which each item is an indicator of only one latent variable, items are theoretically interchangeable with respect to their latent variable; that means, they all measure the same construct.
In theory, the item selection is considered content valid if the items represent a random selection of all possible items that could be used to measure the latent variable.
However, in many cases, the item pool is unknown, so it is not possible to select items at random.
Thus, in practice, when items are not sampled randomly, a scale is considered content valid only if each aspect of the construct definition is reflected by at least one item.
The items of a scale are then used together to measure the latent variable.
When evaluating such a scale empirically, an important goal is to assess whether the questionnaire actually measures the intended construct.
While standard practices report model fit indices and evaluate whether each item has a substantial response variance and item loading, this does not directly answer the question of what the items actually measure.
And even if researchers go the extra mile and reason about the items by interpreting the observed pattern of item loadings (i.e., which items have relatively higher loadings), they often lack a clear strategy for what to compare them to and which patterns would suggest that the items measure the construct as intended.
In the most widely applied test-theoretic models (e.g., factor analytic models), item loadings are interpreted as the extend to which items correlate with, and thus measure, their latent variable [see @lordStatisticalTheoriesMental1968].
Would it not be great, if we had at least one indicator with a strong theoretical justification that this *gold-standard item* is a particularly good measure of the latent variable?
Then we could include the gold-standard item as an additional indicator in the questionnaire’s evaluation and check whether it has the highest, or at least a very high, loading among the items used to measure the latent variable.
If other items load substantially higher than the gold-standard item, one might rightly question whether the scale measures the construct as originally intended, and could start investigating the actual meaning of the latent variable by making sense of the complete loading pattern.

In this study, we examine the idea of evaluating psychological scales with gold-standard items by constructing three psychological questionnaires for the physical traits of *body height*, *body weight*, and *chronological age*.
Extending previous examples of psychological measures of body height [@vanderlindenUnidimensionalLogisticResponse2016; @bortolottiRelevanceAdvantagesUsing2013], we chose these physical traits because, unlike psychological latent variables, they can be directly assessed using valid gold-standard items in the form of numerical self-reports of the respective physical trait (e.g., self-reported body height in centimeters).
We derive and evaluate three assumptions that we argue should hold in our idealized setting with theoretically strong gold-standard items, assuming that our psychological scales achieved valid measurements of the respective latent variables.
To reduce the risk of confounding our findings by how we constructed our psychological scales, we adhere to best practices in the literature on scale construction and item wording.
We also compare questionnaire versions with two different response formats as an additional robustness check.
After presenting our analyses, we discuss the implementation of gold-standard items for evaluating psychological scales for more common psychological constructs.
Furthermore, we discuss the overlap between gold-standard items and single-item measures, which are becoming increasingly common in applied psychological research [@allenSingleItem2022].  

## Theoretical Background

### Gold-Standard Items for Physical Traits

The idea to construct psychological scales for physical traits is not new:
To illustrate the usefulness of logistic item response models, @vanderlindenUnidimensionalLogisticResponse2016 analyzed a teaching dataset from the Netherlands in which body height was measured based on items with two response categories (e.g., "I bump my head quite often.", p. 27).
He notes that this approach is unusual, as body height appears to be a physical variable that can only be measured using a yardstick. 
However, he argues that because differences in height do influence behavior, it is plausible to treat such behavioral indicators as proxies for body height and use them to construct a psychological scale of height. 
Noted as a limitation by the author himself, his dataset did not include a physical height measurement for comparison.

In contrast, @bortolottiRelevanceAdvantagesUsing2013 compared psychological and physical measurements to demonstrate the validity of psychological measurements and the practical utility of psychological measurement models.
They also constructed a 27-item scale to assess body height using a two-category response format.
Participants from Brazil were asked to respond to items such as "Do I think, I would do well in a basketball team?" [@bortolottiRelevanceAdvantagesUsing2013, p. 2350].
At the end of the scale, participants also indicated their actual height in centimeters, a self-reported physical gold-standard item.
Bortolotti et al. compared the parameters estimated from the latent variable body height  with the response on the gold-standard item.
Their analyses revealed a strong correlation (.86, not corrected for disattenuation) between self-reported physical height and the estimated person parameters derived from a two-parameter logistic model of the psychological scale.
However, the gold-standard item did not exhibit the highest loading on the scale [@bortolottiRelevanceAdvantagesUsing2013]. 

Although both studies concluded that their scales successfully measured physical body height, they also identified some items that did not fit the one-dimensional model well, had extreme item difficulties, or did not have a linear relationship with self-reported physical height.
These findings show that even for a relatively simple trait such as physical body height, it is not trivial to construct appropriate items.
In particular, the examples of item misfit in @vanderlindenUnidimensionalLogisticResponse2016 suggest that, in addition to physical height, the items also measured a psychological representation of body height, but the authors did not further investigate possible interpretations for this residual psychological component.

### Item Wording

One important aspect of item construction is item wording.
Surprisingly, @pargentCanMakeIt2019 and @goretzkoNotVeryPowerful2020 showed that the quality of item wording did not, in fact, impact model fit based on commonly used fit indices in confirmatory factor analysis. 
However, clear wording is indisputably essential for understanding an item correctly, highlighting the boundaries of fit indices and emphasizing the importance of conducting cognitive interviews with individuals from the target population when developing items for a new scale [@willisCognitiveInterviewing2005; @willisWhatDo2013]. 
If a person does not understand an items correctly, their response can never be valid, regardless of any model fit indices [for an extreme but illustrating example, see @maulRethinking2017].
Thus, it seems problematic to evaluate the quality of a questionnaire solely by looking at the fit of the latent variable model, item loadings, or reliability estimates.
In this context, @mcneishThornyRelationMeasurement2018 stated that fit indices (e.g., Root Mean Square Error of Approximation, RMSEA; Standardized Root Mean Square Residual, SRMR; and the Comparative Fit Index, CFI) should always be considered in combination with measurement quality (i.e., reliability) and the size of standardized factor loadings.
Gold-standard items offer an additional systematic strategy for scale validation by using the pattern of factor loadings to provide a reference point for evaluating the meaning of other items.

### Response Format

An important topic that hinders the generalization of methodological insights across questionnaires is the potential effect of response formats on scale quality.
@hilbertInfluenceResponseFormat2016 presented initial evidence that different response formats might not measure the same latent variable. They found that the correlation (disattenuated for measurement error) between latent variables measured by identically worded items ranged from .76 to .88 when using scales with two versus five response categories, as well as a visual analogue scale. The question arises: Which of these questionnaires best measures the intended construct?

What we do know in this context is how the number of response categories affects reliability estimates, because a vast body of literature has compared different numbers of response categories for rating-scale items.
We cite several exemplary studies to demonstrate how complex and difficult it is to choose an optimal number of response categories and to highlight what we can conclude from their results.
First, @prestonOptimalNumberResponse2000 reported that two response categories had the lowest retest reliability and relatively poor validity and discriminative power.
They recommended applying rating scales with at least seven response categories. In contrast, @leeSearchOptimalNumber2014 [p. 663] concluded that "caution should be made if a scale has only two response categories, but that limitation may be overcome by manipulating other scale features, namely, scale length or item discrimination".
@weijtersEffectRatingScale2010 recommend rating scales with five fully labeled response categories for samples drawn from the general population.
In their recommendations, the authors considered an extreme response style, responses to reversed items, and acquiescence.
However, @masudaRespondentsLowMotivation2017 found that low-motivated persons tend to use the middle category, implying that a middle category is not advisable. 
Similarly, @bradleyRatingScalesSurvey2015 [p. 8] concluded from their study that "for constructing measures from survey responses, the inclusion of a neutral middle category distorts the data to the point where it is not possible to construct meaningful measures."
All in all, the reviewed literature suggests that to achieve high reliability, seven response categories might be slightly favored, but there is also evidence to omit the middle category due to its inconsistent use.

## The Present Study

We quote from a review on the application of item response models and factor analysis [@tenholtScaleConstructionEvaluation2010, p. 288]: "In our opinion, researchers could take far better advantage of their theoretical knowledge and/or expectations by incorporating their a priori knowledge of the items and scales in the analyses. This should be reflected 1) by a more frequent application of confirmatory techniques, especially in the construction of new scales, and 2) by adding interpretability of factors and item contents to the criteria used for model evaluation."
In line with this statement and the aforementioned research and recommendations, we assess three physical traits to replicate and extend previous findings. 
First, we constructed scales for body height, body weight, and age.
Second, we used items with two response categories to replicate the results for body height reported by @bortolottiRelevanceAdvantagesUsing2013.
Third, we applied an additional format with six response categories, omitting the middle category, which is often overused by low-motivated respondents [e.g., see @masudaRespondentsLowMotivation2017].
We aimed to investigate whether the results of @bortolottiRelevanceAdvantagesUsing2013 hold true for body height and other physical traits, and whether we can identify a residual psychological component in self-report questionnaires of physical traits, as indicated by @vanderlindenUnidimensionalLogisticResponse2016.
Further, we investigate whether the main results are robust across response formats and whether the majority view in the literature is correct in assuming that items with six response categories have higher reliability and, possibly, better validity than items with two response categories [@leeSearchOptimalNumber2014; @prestonOptimalNumberResponse2000; @weijtersEffectRatingScale2010].
In more detail, we argue that if our new scales measure their respective physical trait as intended, we expect to observe the following patterns:

-	*Assumption 1:* The gold-standard items (self-reported physical body height, body weight, and age) should have the highest or at least one of the highest factor loadings among other questionnaire items measuring the respective physical trait (because in one-factor measurement models, a standardized loading can be interpreted as the correlation between the latent variable and the item).

-	*Assumption 2:* Even if gold-standard items have the highest factor loading (and especially if *Assumption 1* does not hold), the measurement of physical traits with questionnaire items possibly captures an additional component that can be interpreted as a psychological representation of the physical trait. When item responses are predicted by the gold-standard item and gender [as we would expect gender differences in self-perception, see @mccrearyGenderAgeDifferences2002], there should remain systematic variance that can be explained by a common latent variable. Ideally, the loading pattern on this residual latent variable should be interpretable to identify the meaning of the psychological component.

-	*Assumption 3a, b:* The correlation pattern among the latent variables of the physical traits (in a three-factor model with correlated latent variables) should closely correspond to the correlations among the gold-standard items (3a). For scales with six response categories, reliability estimates should be higher, and correlations among latent variables and among gold-standard items should be more closely aligned than for scales with two response categories (3b).

\

# Methods

All materials (reproducible manuscript, analysis code, datasets, codebooks, questionnaires) for this manuscript are openly available on the Open Science Framework (OSF) at <https://osf.io/p7492/> [@OsfMaterials2025]. A Quarto Manuscripts website presenting the manuscript and electronic supplementary materials is hosted at <https://florianpargent.github.io/gold-standard-items/>.

## Scale Construction

First, we constructed items for the physical traits of body height, body weight, and age. Age was defined as chronological age in years, corresponding to the time elapsed since a person's birth [@montepareYouReOnly1989; @schwallDefiningAgeUsing2012]. Height was defined as the height of an upright person from the sole of the foot to the top of the head in centimeters, and body weight as the physical mass of a person in kilograms [@martinAnthropometrieAnleitungSelbstaendigen1929]. The initial items were developed by 124 psychology students [through deductive item construction, @burischApproachesPersonalityInventory1984] and 24 persons [through a prototype approach, see @broughtonPrototypeStrategyConstruction1984] who deviated from the German population mean at least one standard deviation in the relevant characteristics (separately for women and men). The 24 persons with extreme trait expressions were asked to think of prototypical behaviors for each construct to assess the whole spectrum of the latent variable. This process resulted in an initial set of 138 items (response categories were not yet tested here).

In a second step, we examined how these items were interpreted and whether they were connected to additional concepts unrelated to the constructs using cognitive interviews. We conducted interviews lasting two to three hours and applied various cognitive procedures, including probing, paraphrasing, concurrent think-aloud, and retrospective think-aloud [@prueferVerfahrenEvaluationSurvey1996; @prueferKognitiveInterviews2005].
The literature on cognitive interviews recommends five to 30 interviews but indicates that the most serious problems in item wording can already be identified with a small number of interviews [@willisCognitiveInterviewing2005; @willisWhatDo2013]. The interviews were conducted with `r nrow(dat_interviews)` people (`r nrow(dat_interviews[dat_interviews$Geschlecht == 1,])` women and `r nrow(dat_interviews[dat_interviews$Geschlecht == 2,])` men) aged between `r min(dat_interviews$Alter)` and `r max(dat_interviews$Alter)` (*M* = `r printnum(mean(dat_interviews$Alter))`, *SD* = `r printnum(sd(dat_interviews$Alter))`). The level of education ranged from high school diploma to university degree. After the cognitive interviews, misleading items were reformulated or eliminated [@faulbaumWasIstGute2009], resulting in 61 remaining items.

In a third step, these 61 items were pilot-tested online with a new sample of initially 456 people.
However, we excluded `r 456 - nrow(dat_pilot)` subjects who had not completed the questionnaire, resulting in a sample of `r nrow(dat_pilot)` participants aged between `r min(dat_pilot$Alter)` and `r max(dat_pilot$Alter)` years (*M* = `r printnum(mean(dat_pilot$Alter))`, *SD* = `r printnum(sd(dat_pilot$Alter))`), including `r nrow(dat_pilot[dat_pilot$Geschlecht == 1,])` women (`r printnum(nrow(dat_pilot[dat_pilot$Geschlecht == 1,]) / nrow(dat_pilot) * 100)`%) and `r nrow(dat_pilot[dat_pilot$Geschlecht == 2,])` men (`r printnum(nrow(dat_pilot[dat_pilot$Geschlecht == 2,]) / nrow(dat_pilot) * 100)`%).
The level of education was distributed as follows: `r round(nrow(dat_pilot[dat_pilot$Bildungsniveau == 1,]) / nrow(dat_pilot) * 100, 2)`% no school-leaving certificate, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 2,]) / nrow(dat_pilot) * 100)`% secondary school-leaving certificate/elementary school or equivalent, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 3,]) / nrow(dat_pilot) * 100)`% secondary school or equivalent, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 4,]) / nrow(dat_pilot) * 100)`% vocational baccalaureate or high school diploma, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 5,]) / nrow(dat_pilot) * 100)`% college degree or university degree, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 6,]) / nrow(dat_pilot) * 100)`% doctorate or habilitation.
Of all respondents, `r printnum(nrow(dat_pilot[dat_pilot$Muttersprache == 1,]) / nrow(dat_pilot) * 100)`% stated German as their native language.
Based on these survey responses, we excluded items if a) their main item loading did not load the intended factor in three-dimensional exploratory factor analyses, b) their main and secondary loadings were nearly equal, or c) their main loading was less than or equal to .30. Additionally, if (d) items had very similar content, items with lower loadings were excluded.
More details on the item construction process can be found in @eichhornItem2019.
We recomputed the exploratory factor analyses, item total correlations, and reliability estimates that were computed in this final item selection stage and report them in our electronic supplementary materials (ESM C). Based on these criteria, 12 final items were selected for each physical trait (see @tbl-5).[^notewording]
For each of the three questionnaires, we created two versions – one with two response categories combining verbal labels ("does not apply" and "applies") with numeric anchors (numbers 0 and 1) and one with six response categories combining verbal endpoints ("does not apply" to "applies", only endpoints were labeled) with full numeric anchoring (numbers from 1 to 6).
The 2-point scale version was included because we wanted to replicate the results by @bortolottiRelevanceAdvantagesUsing2013 and @vanderlindenUnidimensionalLogisticResponse2016, who also used a binary response format, and because this is an important response format in clinical psychology and medicine. The 6-point scale version was used as a robustness check to ensure that our results hold for ordinal response formats, which are common in practice, and to replicate the common finding that reliability estimates are higher for scales with more than two response categories [@prestonOptimalNumberResponse2000].
Using six response categories is an obvious synthesis of the literature, favoring a higher number of response categories [@prestonOptimalNumberResponse2000] whilst avoiding a middle category [@masudaRespondentsLowMotivation2017].
However, we acknowledge that the evidence is not clear-cut and other experts prefer five or seven categories.
We decided against including additional questionnaires with other response formats to ensure a sufficient sample size for each version.

[^notewording]: Because the described procedure did not return at least 12 items for all scales, the decision was made to keep two weight items (W3 and W7) and two age (A7 and A10) with very similar content. Compared to the pilot test, one height item (H7) and one weight item (W7) were slightly rephrased to simplify the wording and reduce similarities in sentence structure with other items in the scale.

## Statistical Analysis

All analyses were conducted in `r R.version$version.string`. A full list of software versions can be found in @apx-3. The data were analyzed using confirmatory factor analysis with the package *lavaan* [@R-lavaan]. We used the weighted least squares, mean and variance adjusted (WLSMV) estimator, treating the questionnaire items as ordinal and the self-reported physical gold-standard items body height, body weight, and age as continuous variables.
First, we specified one-factor models with no error correlations and with correlated errors.
In both models, the gold-standard items and the other 12 items were specified as indicators of a single latent variable.
Second, to test whether an interpretable latent variable remains after controlling for the gold-standard item and gender, one-factor models were specified with a single latent variable, with the questionnaire items additionally predicted by the gold-standard item and gender.[^noteresidualmodel]
Third, to compare the correlations between the latent variables of the physical traits with the correlations between the gold-standard items, one full three-factor model without correlated errors was estimated, in which only the questionnaire items load on their respective latent variable, and correlations are estimated between the latent variables, between the gold-standard items, and between the latent variables and the gold-standard items. We also conducted reliability analyses using the package *MBESS* [@R-MBESS] and report McDonald's Omega as the reliability estimate of internal consistency for each scale.
All analyses were ran separately for both response formats (2-point and 6-point scales). 

[^noteresidualmodel]: Under the assumption that the gold-standard item closely represents the true physical trait, this analysis can be interpreted as a two-dimensional factor model where the latent variable is a second (psychological) factor independent of the physical trait (after controlling for gender). In our special case of investigating physical traits, we would argue that this analysis is more informative about the dimensionality of the scales than (a more common) exploratory factor analysis.

The analyses reported in the current manuscript were not preregistered.
However, the data we used have previously been analyzed in the first author's German dissertation [@eichhornItem2019]. As part of this dissertation, a preregistration was published at <https://osf.io/cz3uv/?view_only=9cac02db231b48629fea9ae53c3038b9>. The preregistration describes the planned data collection procedures and sample sizes, specifies the scale construction process, including the cognitive interviews and item selection based on the pilot sample, and registers the design of the questionnaires used in the validation sample, including the response format of both versions.
In the current manuscript, we performed all of these steps as preregistered.
However, our statistical analyses deviated from those listed in the preregistration.
The reason for this deviation is that our general understanding of what we can learn from scales of physical traits about the construction of psychological scales has evolved continuously since preregistration, and we deem the analyses in the current manuscript more elegant for presenting our ideas than the originally preregistered analyses.
In fact, the preregistration did not include the concept of gold-standard items or the detailed assumptions discussed in this manuscript. Instead, the registered research question was kept vague: *"The main research question is how well the items represent the real score values. More precisely, is it possible to construct a questionnaire, following the best practice of test construction, to measure a variable that we claim to measure."*
The results of the preregistered analyses are fully reported in @eichhornItem2019. Note that no results in this manuscript are in conflict with any of the preregistered analyses. Both the current manuscript and the preregistration state that all analyses should be considered exploratory.
<!-- The preregistration deliberately omitted any decision rules specifying which concrete results would lead to which conclusions. -->

## Sample

The total sample of our main study consisted of `r nrow(dat_desc)` participants aged between `r min(dat_desc$Alter_realW)` and `r max(dat_desc$Alter_realW)` years (*M* = `r printnum(mean(dat_desc$Alter_realW))`, *SD* = `r printnum(sd(dat_desc$Alter_realW))`), including `r nrow(dat_desc[dat_desc$Geschlecht == 1,])` women (`r round(nrow(dat_desc[dat_desc$Geschlecht == 1,]) / nrow(dat_desc) * 100)`%) and `r nrow(dat_desc[dat_desc$Geschlecht == 2,])` men (`r round(nrow(dat_desc[dat_desc$Geschlecht == 2,]) / nrow(dat_desc) * 100)`%). 
The overall sample consisted of two independent subsamples, which were divided into the conditions with two ($N$ = `r nrow(dat_desc[dat_desc$categories == "2 categories",])`) and six ($N$ = `r nrow(dat_desc[dat_desc$categories == "6 categories",])`) response categories.

Participants were recruited in trains, colleges, universities, adult education centers, fitness studios, and various public places in Germany and Austria in November and December 2017. Participation was voluntary and without reimbursement. Each participant was given a piece of paper informing them about the voluntary and anonymous nature of their participation, the purpose of the study, and the data to be collected.
Upon providing consent, participants received one of two paper-and-pencil questionnaire versions: one using the 2-point and the other using the 6-point response scale.
The two versions were alternated as questionnaires were handed out to participants.
When a participant returned the questionnaire, the facilitator immediately checked for missing values and, if any were found, politely asked the participant to complete the missing questions.
With this procedure, we achieved complete responses for all questionnaires.
No power analysis was performed to determine the sample size. Instead, the goal was to collect at least 500 subjects per response format condition over a period of six weeks. No data was analyzed before data collection ended.
The final sample size of this study is typical of those used in current validation studies that publish diagnostic results. According to @goretzkoEvaluatingModelFit2024, the sample sizes used in typical validation studies in the journal Psychological Assessment from 2015 to 2020 were as follows: about 38 percent used sample sizes of 401 to 1000, and 25 percent sample sizes larger than 1000.

@tbl-1 shows the distribution of age, gender, level of education, and native language for each response format. As a result of the randomization procedure, the two subsamples are very similar. Due to the left-skewed age distribution and outlier values, we report both the mean and the median. 

```{r}
#| label: "tbl-1"
#| tbl-cap: Sample characteristics for the questionnaire with two and six response categories
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: $SD$ = standard deviation; $IQR$ = interquartile range.

results$table1
```

\

# Results

## *Assumption 1:* The gold-standard item for body height, weight, and age should have the highest loading on its latent variable.

@tbl-2 displays the measurement models for the three scales for body height, body weight, and age for two and six response categories each.

```{r}
#| label: "tbl-2"
#| tbl-cap: Standardized item loadings (correlations with the latent variable) for two and six response categories 
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: CFI = Comparative Fit Index (scaled); RMSEA = Root Mean Squared Error of Approximation (scaled); SRMR = Standardized Root Mean Residual. Scaled $\chi^2$, scaled $df$ (degrees of freedom), and scaled *p*-values are reported. Correlations with the latent variable that are higher than those of the self-reported physical item are printed in bold. The standardized item loadings for the self-reported physical items are presented in a grey-shaded box together with 95% confidence intervals.

results$table2
```

\

Overall, both response formats produced very similar loading patterns, but scales with two response categories yielded slightly higher loadings than scales with six response categories for most items.
All model fits were within the expected range for psychological questionnaires [@goretzkoEvaluatingModelFit2024].[^dynamicfit]
Questionnaires with two response categories showed slightly better fit than those with six categories with respect to the CFI and the RMSEA, but slightly worse fit with respect to the SRMR. 
The best model fit was observed for the psychological scales for body height and weight with two response categories.

[^dynamicfit]: For readers particularly interested in absolute model fit, we also report dynamic fit index cut-offs [@mcneishDynamicFit2021] for the one-factor models of height, weight, and age for two- and six-response categories in our electronic supplemental materials (ESM A).

```{r}
# correlation of loadings between cfa models with and without correlated errors
r_loadings <- cor.test(
  # use absolute values because the items were not recoded for cfa models
  abs(results$load_df_nomod$est.std), abs(results_secondary$load_df_mod$est.std), 
  method = "pearson")
r_loadings <- apa_print(r_loadings)$table
```

For the body height scales, the self-reported physical height loaded higher or similarly high on the latent variable compared to the questionnaire items.[^notetest]
However, this pattern differed for the weight and age scales, where several items loaded substantially higher on the latent variable than the physical items:
For weight, the items 4 ("I am obese.") and 5 ("I weigh a lot.") had especially high loadings on the latent variable for both questionnaire versions, as did item 7 ("I have already lived most of my life.") for age.
The loading pattern for the weight and age scales, with lower loadings for the gold-standard items, suggests that these scales do not measure the intended constructs of physical weight and physical age. 
Even after allowing for correlated errors as suggested by standard modification indices, the loading patterns did not improve (see @tbl-5). Loading patterns with and without modifications were correlated at `r r_loadings$estimate` (*p* `r r_loadings$p.value`) across all questionnaires (body height, body weight, age) and response variants (two and six categories).

[^notetest]: Note that comparing point (or interval) estimates of factor loadings is not equivalent to a formal hypothesis test testing whether the true loadings of the gold-standard item are higher than all other loadings. Because our study is not confirmatory, we see no added value in computing and reporting such hypothesis tests, which is not trivial and would unnecessarily complicate our presentation of results. To give interested readers a better intuition about the plausible ranges of true factor loadings and the measurement uncertainty in our estimates, we provide 95% confidence intervals for all factor loadings from @tbl-2 in our electronic supplementary materials (ESM A).

## *Assumption 2:* The measurement should have a systematic psychological component, and an interpretable latent variable should remain after correcting item responses for the gold-standard items and gender.

@tbl-3 displays item loadings on the latent variable when controlling for the self-reported physical item and self-reported gender.

```{r}
#| label: "tbl-3"
#| tbl-cap: Standardized item loadings on the latent variable for two and six response categories, controlling for the self-reported physical item and self-reported gender
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: Standardized regression weights greater than .60 in absolute values are printed in bold. Latent = standardized item loading on the respective latent variable (height, weight or age); Physical = standardized regression weight, predicting the item response by the respective self-reported physical measures (height, weight or age); Gender = standardized regression weight, predicting the item response by the self-reported gender (positive values imply higher item responses for men).

results$table3
```

\

For body height, we obtained low item loadings on the latent variable but high regression weights with the gold-standard item of physical body height. In particular, the third item ("Chairs and tables are usually too low for me.") exhibited the highest loading on the latent variable for both response formats. In contrast, item 11 ("I have to stand at the front of group photos so that I can be seen clearly.") and item 12 ("When I hug other people in greeting, I have to bend downwards.") were best predicted by the self-reported physical body height for both response formats.[^loadingsgreaterone] This pattern does not convincingly confirm the existence of a psychological latent height component after controlling for the self-reported physical item and gender.

[^loadingsgreaterone]: Note that although in the model for height with two categories (controlling for the physical item and gender) the absolute standardized regression weights of the physical item predicting items 11 and 12 were estimated to be greater than one, this does not indicate a problem with the model. All models converged and the diagnostics used by the *lavaan* package [@R-lavaan] did not report any issues. In these models, each item is predicted by three variables (latent variable, physical item, gender). Thus, the standardized (partial) regression weights cannot be interpreted as correlations and do not have to fall within the [-1,1] range.  

For body weight, items with high loadings on the latent variable also exhibited strong associations with the self-reported physical body weight. Item 4 ("I am obese.") had the highest loading on the latent variable for both response formats. Item 5 ("I weigh a lot.") was explained best by the self-reported physical body weight. Item 9 ("I have a lot of space between the armrests in airplane seats.") had a low loading on the latent variable but was moderately predicted by the self-reported physical body weight for both response formats. Notably, item 11 ("If I have the choice between the elevator and the stairs, I take the elevator.") was not related to either the self-reported physical item or the latent variable for both response formats, indicating that it may represent a more health-related attitude. Taken together, the resulting psychological latent weight component seems hard to interpret.

For age, we observed the biggest discrepancy between items with high loadings on the latent variable and items best predicted by self-reported physical age. Item 3 ("I have a lot of life experience.") and item 9 ("I have years of work experience.") did not load on the latent variable after controlling for physical age and gender but were predicted by self-reported physical age for both response formats. In contrast, the three items most prototypical of the latent variable were item 2 ("Over time, my mental capacity has decreased."), item 4 ("Over time, my ability to react has decreased."), and item 5 ("Over time, my memory has deteriorated.") for both response formats. Thus, the psychological latent age component might be interpreted as mental age, but not all items load substantially on this general factor.

When examining self-reported gender, there were moderate standardized regression weights for some body height items (e.g., item 8 "Pants are often so short for me.") and body weight items (e.g., item 6 "I need to lose weight."). These items may pose problems when applied to both men and women [differential item functioning\; see @hilbertWhatMeasureEmpirical2022, for a comparable case]. Notably, standardized regression weights for self-reported gender predicting age items were mostly low.

## Assumption 3a, b: The correlation pattern among the latent variables of the physical traits should match the correlation among the gold-standard items (3a). For scales with six response categories, reliability estimates should be higher, and correlations among latent variables and among gold-standard items should be more closely aligned.

As shown in @tbl-4, the correlations among the latent variables do not match the correlations among the self-reported physical items. Only height and age showed relatively similar correlations among latent variables and among physical items. However, the correlations between physical weight and physical age were overestimated by the correlations between the latent variables of weight and age, and the correlations between physical height and physical weight were underestimated by the correlations between the latent variables of height and weight. Most notably, correlations did not differ systematically between the questionnaires with two and with six response categories. Descriptively, the latent correlations seemed to reproduce the physical correlations slightly better for the questionnaires with two response categories. However, reliability estimates (Omega) were lower for two response categories compared to six response categories.

```{r}
#| label: "tbl-4"
#| tbl-cap: Correlations among the latent variables of the physical traits, correlations among the corresponding self-reported physical items, and reliability estimates, for two and six response categories
#| ft.align: left
#| apa-note: !expr 'paste0("Correlations among the latent variables are shown above the diagonal (in bold), and correlations among the self-reported physical measures are shown below the diagonal. For each response format, the reported correlations were obtained from a latent variable model that included all self-reported physical items and all latent variables with their assigned items. The models showed the following fit: scaled chi-square (six response categories) = ", printnum(results$fullmodelfit6["chisq.scaled"]), ", $df$ = ", results$fullmodelfit6["df"], ", $p$ ", printp(results$fullmodelfit6["pvalue.scaled"]), ", scaled CFI = ",  printnum(results$fullmodelfit6["cfi.scaled"], gt1 = FALSE), ", scaled RMSEA = ", printnum(results$fullmodelfit6["rmsea.scaled"], gt1 = FALSE), ", SRMR = ", printnum(results$fullmodelfit6["srmr"], gt1 = FALSE), "; scaled chi-square (two response categories) = ", printnum(results$fullmodelfit2["chisq.scaled"]), ", $df$ = ", results$fullmodelfit2["df"], ", $p$ ", printp(results$fullmodelfit2["pvalue.scaled"]), ", scaled CFI = ", printnum(results$fullmodelfit2["cfi.scaled"], gt1 = FALSE), ", scaled RMSEA = ", printnum(results$fullmodelfit2["rmsea.scaled"], gt1 = FALSE), ", SRMR = ", printnum(results$fullmodelfit2["srmr"], gt1 = FALSE), ". Reliability estimates (Omega) are shown on the diagonal (gray-shaded cells). * $p \\leq$ .05, ** $p \\leq$ .01, *** $p \\leq$ .001.")'


results$table4
```

\

# Discussion

## Summary

The goal of this study was to evaluate newly constructed psychological scales with gold-standard items in the special setting of physical traits (body height, body weight, and chronological age) where theoretically strong gold-standard items are available as a numerical self-report of the physical trait.
Using confirmatory factor analysis, we found that contrary to our assumptions, even in this ideal setting, gold-standard items did not have the highest loading on the corresponding latent variable for all physical traits.
After controlling for the gold-standard item and gender, a residual psychological component was found for all traits, but the meaning of this latent variable was hard to interpret at best.
The correlations between the latent variables also did not closely match the correlations between the gold-standard items.
All results were highly similar for questionnaire versions with two and six response categories, although reliability estimates were slightly lower for the versions with two response categories.

## Gold-Standard Items for Physical Traits

Despite the favorable setting of constructing psychological scales for physical traits and an extensive construction process, gold-standard items did not fully work as expected with respect to our theoretical assumptions.
Only the gold-standard item for body height – for six, not for two response categories – had the highest correlation with the latent variable.
The scales for body weight and chronological age did not produce the highest correlation between the latent variable and their gold-standard items relative to the other items of the scale.
Considering both the size and the measurement uncertainty of the factor loadings, it seems evident that the gold-standard items for weight and age load substantially lower on the latent variable than the best items of the respective scale.
This finding clearly questions, whether our psychological scales for weight and age measure their physical traits as intended.
Unfortunately, we could not fully clarify what these scales measure instead. 
When we controlled item responses for the gold-standard items and gender, we found the remaining latent variable hard to interpret. 
Previous literature hints that measuring physical attributes through psychological questionnaires is not always connected to a well defined psychological latent variable guiding behavior [@hilbertWhatMeasureEmpirical2022; @vanderlindenUnidimensionalLogisticResponse2016].
Also in our study, it remained unclear if a psychological latent variable beyond body height and weight was measured and how such a latent variable could be interpreted (for this purpose, we also inspected the biggest correlated errors in the one-factor models reported in @tbl-5, but without much success).  
Only for the age scales did we find some plausible indications that the latent variable could be interpreted as cognitive or psychological age [@barakCognitiveAgeNonchronological1981].
The three age items with the highest loadings on the residual latent variable where all related to mental decline but there were also many items without a substantial loading on this latent variable.
Only for age did we observe the peculiar pattern that items were either well predicted by the physical item or had high loadings on the residual latent variable, but not both.
In contrast, the weight items with the highest loading on the residual latent variable were also predicted substantially by the physical item.
For height, all items were well predicted by the physical item and had rather small but consistent loadings on the residual latent variable.
Overall, the unclear interpretation of the residual latent variables is consistent with our finding that the correlations between the latent variables of the three scales did not closely match the correlation between the corresponding gold-standard items (with little differences between response formats) and we did not find a clear interpretation of the altered pattern.
Combining the evidence from all analyses, only the psychological scales for height performed (almost) up to our expectations and we only consider them to be appropriate measures of their respective physical trait body height.

In light of these issues, it is important to assess whether some decisions in our construction process might have led to unique problems with our scales.[^extremewording]
It is thus useful to compare our results with the study from @bortolottiRelevanceAdvantagesUsing2013, who previously applied the same procedure with 27 items with two response categories to investigate a gold-standard item for body height.
They found a correlation of .86 between the sum score of their scale with self-reported height which closely matches our correlation of the gold-standard height item with the latent variable (two response categories: `r results$load_df_nomod |> filter(rhs == "Koerpergroesse_realW" & categories == 2) |> pull(est.std) |> printnum(gt1 = FALSE)`, six response categories: `r results$load_df_nomod |> filter(rhs == "Koerpergroesse_realW" & categories == 6) |> pull(est.std) |> printnum(gt1 = FALSE)`). 
They also reported items with descriptively equal or higher correlations (biserial correlations) with the sum score than the self-reported physical item (Pearson correlation).
The comparison does not suggest that our scales have unique problems, considering that we were able to conceptually replicate @bortolottiRelevanceAdvantagesUsing2013 with our independently developed questionnaire.

[^extremewording]: For example, one reviewer questioned why many of our items use quite extreme item wording (e.g. "I have already lived most of my life") and pondered whether this might explain why our scales did work as expected. However, our cognitive interviews and pilot tests suggested that -- maybe surprisingly -- these items worked best to assess height, weight or age.

It is also noteworthy that our results where surprisingly robust with respect to different response formats as we found very similar results for questionnaire versions with two and six response categories.
As expected, reliability estimates were slightly higher for scales with six response categories compared to two categories [@prestonOptimalNumberResponse2000].
But the results with regard to model fit and validity, indicated as correlations between latent variables compared to the correlation between gold-standard items, were mixed.
Some fit indices suggested slightly better fit for items with two response categories and some for six categories (although the difference were rather small).
The same holds true for the differences between the correlations of the gold-standard items and the correlations of the latent variables.
Except for reliability, our results do not clearly favor either two or six response categories. 
Although we would not suspect strongly different results for five or seven response categories, we cannot with certainty generalize our results towards response formats that include a middle category (we only used formats without a middle category) or response formats where all categories are labeled (we only labeled the endpoints).
Hilbert et al. [-@hilbertInfluenceResponseFormat2016; -@hilbertWhatMeasureEmpirical2022] showed that the same items with a different number of response categories do not necessarily measure the same latent variable.
Thus, there is always the possibility that the selection of the response format changes validity.
We used a 6-point response format because this is our own personal preference which aligns with the part of the literature advising against using a middle category.
The 2-point response format was chosen because it is a qualitatively different format that is extensively used for symptom questionnaires in clinical psychology and medicine.
When we consult on how to constructing psychological scales, we always advise our clients that the number of response categories should be considered carefully.
An intensive cognitive pretesting phase can help to understand how people use and understand the categories and empirical studies can help to choose number of response categories which provide better validity or/and reliability or/and factor structures [@willisWhatDo2013].
In the current study, the pretesting as well as the final results suggest that both applied response formats worked reasonably well.


## Gold-Standard Items for Psychological Traits

Based on our findings on using gold-standard items to evaluate psychological scales for physical traits, we want to discuss whether a similar strategy could also be used in the more common task of constructing psychological scales for psychological traits, where theoretically strong gold-standard items are more difficult to come by.

In psychology, we try to use precise names for our latent variables such as as emotional intelligence, self-efficacy, conscientiousness or narcissism.
It might therefore seem easy to always subject the naming of the latent variable to a kind of gold-standard item.
But would we really expect that in a questionnaire that measures conscientiousness, an item like *"I am a narcissist."* [see @konrathDevelopmentAnd2014] best reflects the construct *narcissism* and thus has the highest factor loading? 
In this context, we see great overlap with the psychological research on single-item measures:
Single-item measures (i.e. measuring a psychological construct with a single question in rating scale format, which often uses slightly longer wording and provides additional context in its instruction) are increasingly used in psychological research when constructs have a rather narrow definition and there are strong practical reasons why longer multi-item scales cannot be applied without problems [@fuchsUsingSingle2009].
However, it has been emphasized repeatedly that rigorous validation is equally important for single item measures than for all psychological scales [@allenSingleItem2022].
In this literature, one common piece of evidence how to examine the validity of a newly constructed single item measure is to examine the loading of the single item measure in a one-factor model including both the single item measure and the items from an established multi-item scale for the same psychological construct [@fisherDevelopingInvestigating2016; @matthewsNormalizingUse2022].
This is exactly the same logic we used in our study of gold-standard items for physical traits.

Thus, when constructing a new psychological scale, the researcher could always check whether a validated single-item measure for the same psychological construct is available in the literature.
Those single-item measures would be natural candidates for gold-standard items that could be included in the validation study of the new scale.
Although the literature on single-item measures argues that a good single-item measure should load highly on the latent variable shared with the multi-item scale, it does not require the single-item measure to have the highest or equally high loading than the best items of the scale [@fisherDevelopingInvestigating2016; @matthewsNormalizingUse2022].
We would argue that in most circumstances, it would nonetheless suggest issues with the newly constructed scale if the single item measure does not have a high loading compared to the other items.
But note that there is empirical evidence that such analyses would detect problems in a substantial number of scale construction processes even when using a much lower bar.
In @fisherDevelopingInvestigating2016, eight out of 18 newly constructed single-item measures had lower loadings than all items of the corresponding multi-item scale and one single-item measure had a low absolute loading less than 0.3.
In @matthewsNormalizingUse2022, seven out of 91 newly developed single-item measures did not even load significantly on the factor shared with the corresponding multi-item scale, loaded in the wrong direction or had a low absolute loading less than 0.3.[^matthews]
Even if there is no consensus on how big the loading of the single-item measure should be in order to conclude that everything is fine [@allenSingleItem2022], we would argue that most experts would agree that at least in the cases reported above, there must be some problem either with the single-item measure, the multi-item scale or both.

[^matthews]: Unfortunately, @matthewsNormalizingUse2022 do not report how often the single-item measure had the highest estimated loading compared to the items from the multi-item scale and it is not possible to extract this information from their paper or supplemental materials.

What would be plausible reasons why a single-item measure should not have the highest loading relative to the items from a corresponding multi-item scale?
The literature argues that single-item measures should be most effective when the psychological construct is narrow in scope and complexity [@fuchsUsingSingle2009; @matthewsNormalizingUse2022].
For such homogeneous constructs, it should be simpler to construct a single item that captures the essence of the construct and is interpreted similarly by the target population.
In this sense, our application of constructing psychological scales for the physical traits height, weight, and age should have been a very favorable setting.
For more heterogeneous and complex constructs like personality traits, it should be harder to capture the whole construct in one item without ambiguity [although the possibility that abstract single-item measures might be useful for the most complex constructs where it is almost impossible to add one item for each content aspect has also been discussed, see @fuchsUsingSingle2009].
If done nonetheless, we must assume that the single-item measure contains a unique weighting of the multiple content aspects of the construct.
Thus, we would only expect the single-item measure to have a very high or the highest loading relative to other items of a multi-item scale, if the aspect of the construct that is most strongly represented by the single-item measure also has the biggest contributions in the corresponding multi-item scale.
However, note that in situations where we would not expect the highest loading for the single-item measure because the measured construct is rather heterogeneous, it can be questioned whether a one-dimensional latent variable model should be applied for the items of such a scale anyway because there will probably be more than one factor and/or correlated errors.
To summarize, we agree with the literature that one should not blindly expect a single-item measure to have the highest loading when combined with the items of a corresponding multi-item scale without further consideration.
Instead, we recommend researchers to carefully compare the construct definitions of the newly constructed multi-item scale and the existing single-item measure before performing the validation study.
Based on this theoretical analysis, it should be possible to form a rough hypothesis about the expected size for the loading of the single-item measure that is more informative than just assuming that the loading has to be greater than zero.

But what can be done in practice if there is no validated single-item measure available that closely matches the construct definition of our newly constructed scale?
Can we still use a gold-standard item in a less strict sense?
We argue that there will still be settings in which this makes sense and finding appropriate gold-standard items is rather straightforward. 
For example, consider adjectives for measuring personality and let us assume that we try to measure the latent variable *interpersonal warmth* with the following adjectives: *affectionate*, *friendly*, *talkative*, *unprejudiced*. We ask how well each adjective describes yourself from *not at all* (1) to *fully and entirely* (6) with six response categories. 
If these items actually measure interpersonal warmth, they should also correlate with the adjective *warm* measured with the same response format.
Even more, we would argue that one should at least question the definition and intended verbal label of the construct, if it turns out that this item does not have the highest loading in a one-factor model when combined with the other items of the scale.
Otherwise, a different construct is probably measured; e.g., *friendliness* if the adjective *friendly* has the highest loading on the latent variable.
Thus, the *warm* item could be considered a gold-standard item quite similar to our examples with physical traits.
This brings us to the interesting question, whether the gold-standard item in this case should be part of the final scale or not.
We would argue that this depends on the concrete setting and cannot be answered in general.
Assume our newly constructed *interpersonal warmth* scale was always supposed to also include an item that is the adjective *warm*. 
This item would clearly match the intended label of the construct most directly.
But even if we did not originally intend to include an item called *warm* in this scale, the structure of the questionnaire in which all items are adjectives almost requires us to test the most straightforward item possible and examine its loading.
In the end, it will always be up to the researcher to decide which items are appropriate to use as part of the scale in practice and which items are only used in the validation of the scale.

Despite these examples, we acknowledge that there will probably be many instances of constructing new psychological scales where theoretically strong gold-standard items are not available and our suggested evaluation strategy cannot be readily applied.
This should not be a problem because it does not theoretically invalidate the already discussed settings in which the strategy is meaningful.
Note that our evaluation strategy with gold-standard items is only a special case of a more general principle in test construction:
Whenever you construct a new psychological scale, you should always use your theoretical knowledge about the definition of the intended construct, its nomological network, and intended practical use cases for the new scale to produce hypotheses about the scale and its items that are at least partly open to empirical testing.
As a metaphor, think of a psychotherapist that continuously forms and revises hypotheses about the causes of symptoms and the psychological structure of his patients.
Although those hypotheses can never be verified with certainty and it is rarely useful to apply formal statistical hypothesis testing, they are nonetheless essential to form an understanding of the patient and how they function in their daily life.
The more hypotheses about our new scale are available and the stronger the theoretical rationale why we would expect a certain pattern, the more holistically we can empirically evaluate whether we actually measure the intended construct, and the better we should be able to convince ourselves and the scientific community that we have constructed a useful new scale.
Assessing the loading of self-postulated gold-standard items is just one small example of such a hypothesis, and how convincing that hypothesis is will always depend on the concrete example.

Considering that we did not consistently manage to construct scales where gold-standard items showed the highest factor loading even for the optimal setting of physical traits, we expect it to be even more difficult to achieve the theoretically desirable loading pattern when constructing scales for psychological traits.
Hopefully, we could demonstrate convincingly why we still think that gold-standard items can be a useful tool for validating new psychological scales.


<!-- And even if we empirically found out that it does, this would lead to the difficult questions whether such gold-standard items should only serve for validation purposes or also be included in the final scale. -->
<!-- Probably, the understanding of the items or individual terms within the items (e.g. conscientious) can vary between people. With language, formulations are often open to multiple interpretations and depend on the knowledge, experiences, and context of reference of the participants from the target group.  -->

<!-- Spörrle, M., & Bekk, M. (2014). Meta-analytic guidelines for evaluating single-item reliabilities of personality instruments. Assessment, 21(3), 272–285. -->

<!-- Hughes, D. J. (2018). Psychometric validity: Establishing the accuracy and appropriateness of psychometric measures. In P. Irwing, T. Booth & D. J. Hughes (Eds.), The Wiley handbook of psychometric testing: A multidisciplinary approach to survey, scale and test development. Chichester, UK: Wiley. -->
<!-- Until this point, our focus has been on establishing “internal” psychometric characteristics of the proposed single-item measures, that is, do they accurately and precisely measure the construct of interest (Hughes 2018). -->
<!-- For example, in Hughes’ (2018) two-step model, psychometric developers are charged with answering two fundamental psychometric questions sequentially: “am I measuring what I want to measure?”, as supported by content, response process, and structural evidence, and “is my measure useful?” as supported by convergent, discriminant, and concurrent validity evidence, among other types of evidence (Hughes 2018, p. 752). -->


<!-- The results differed for the other latent variables of body weight and age, which exhibited lower correlations between the latent variable and their gold-standard items. This seems problematic as these items were designed to be the "gold" measure of the latent variable and should ensure a consistent interpretation. Thus, we should carefully reflect what this finding means for item construction for psychological scales of non-physical traits. If this basic requirement is not met, even for traits that seem rather straightforward to measure, what about more complex constructs? To avoid a misleading interpretation of a latent variable, it might be very helpful to formulate a priori hypotheses about the importance of the constructed items as we did here to test the construct validity of a test. If we, for example, want to measure *interpersonal warmth* as a big five facet and construct items that describe this facet, an item that most directly measures warmth should have its highest loading on the latent variable, otherwise the interpretation of the latent variable is not justified. -->

<!-- If the item "warmth" as gold-standard item perfectly capture the latent trait, why not using it? @allenSingleItem2022 discussed this in more detail. The utility and efficiency of single item measures seem to be an advantage of using a single-item measures, especially the administration, costs and the higher motivation of participants filling out the questionnaires. The authors state that single-item measures are acceptable when constructs are unidimensional, clearly defined, and narrow in scope. The authors argue that against single-item measures can be said that the reliability is at least unknown and that a single item-measure cannot capture the content of a complex construct. Thus, even if we have gold-standard items, we should not easily omit multi-item measures. The main purpose of many questionnaires is measuring the value of a person of a given construct. Thus, the instrument should differentiate between persons (more than five response categories) and should have reliability as high as possible. In many cases this can achieved best using questionnaires with multi-item measures. -->

<!-- It could be argued that a subsample of our used 12-item set might lead to different conclusions and empirical results. This result could occur. But this is a feature not a bug using gold-standard items. The solution with the best interpretability regarding content validity should be considered. We argue that even such a selection process would benefit using gold-standard items. The change of the loading patterns can help to see if a solution leads to a considerable change of the gold-standard-item factor loading. TODO -->

<!-- Previous hints suggest that measuring physical attributes through psychological questionnaires is not always connected to a psychological latent variable guiding behavior [@hilbertWhatMeasureEmpirical2022; @vanderlindenUnidimensionalLogisticResponse2016]. Similarly, in our study, it remained unclear if a psychological latent variable beyond body height and weight was measured and how such a latent variable could be interpreted. Only for age there was a latent variable, which can be interpreted as cognitive or psychological age [@barakCognitiveAgeNonchronological1981]. Furthermore, it seems helpful to include additional items, that are not intended to be measured but may further explain the item responses of interest, such as gender or items from the nomological net to reveal possible dependencies and to decide whether these dependencies are in line with the definition of the latent variables. TODO -->

<!-- This approach has the following limitation. In practice, we are used to interpret point estimates of factor loadings. According to @hirschfeldSelecting2014, almost all sample sizes are too small to obtain stable factor loadings or beyond that to interpret differences in factor loadings. Thus, large sample sizes and the consideration of confidence intervals are needed. How large is large enough? This cannot be easily answered, since @wolfSampleSize2013 have shown it is dependent of many parameters e.g., model complexity, number of items, missingness. Another limitation and explanation and for lower loadings of the items constructed compared to the physical items is, that some items have low item difficulties and therefore a restricted variance. During the item construction phase items with somehow extreme formulation worked best to assess height, weight or age (e.g. "I have already lived most of my life"). TODO -->

<!-- Thus, we suggest using gold-standard items as described above. It should be noted, however, that it is critical not to implement the gold-standard item in the final scale since we would then create a part-whole relationship. This no desirable situation since all test models (classical and IRT models) assume that the probability of a positive response of a person to an item should not depend on this person’s response to any other item [@debelakTestingLocalIndependence2020]. TODO -->

<!-- Based on the results of the present study, we advocate the inclusion of gold-standard items, i.e. items that are supposed to measure the intended construct most directly, to check the interpretation of latent variables in the construction of psychological questionnaires. -->

<!-- **Benefits:** -->

<!-- - Gold-standard items can be implemented very easily without extensive costs and time requirements -->
<!-- - Gold-standard items aid to process to name a latent variable.  -->
<!-- - Gold-standard items can help to develop single-item measures.  -->

<!-- **Caveats:** -->

<!-- -	The loadings of the gold-standard items may change depending on the item subgroup used. This, in turn, can help to clarify the measurement objective or can represent an alternative option for item selection. Present the item set. A solution in which the gold standard item has a comparable loading to other marker items on the latent variable can be easily interpreted in terms of the construct definition and may be preferred over other item sets.  -->
<!-- -	The sample sizes should be large enough [see @wolfSampleSize2013; @hirschfeldSelecting2014] to obtain stable estimates of loadings and confidence intervals should be used to make inferences about the loading of the gold standard variable compared to other variables. A rule of thumb could be that only non-overlapping confidence intervals could be evidence paying attention to the interpretation. -->

## General Lessons and Recommendations

Our current failure to construct psychological scales for physical traits that fulfill all our self-imposed requirements despite applying a rigorous best-practice construction process can be seen as the latest installment in our line of research on scale construction rules and their apparent problems [@goretzkoNotVeryPowerful2020; @pargentCanMakeIt2019; @hilbertWhatMeasureEmpirical2022; @hilbertInfluenceResponseFormat2016].
Our work should prompt reflection and reconsideration of standard procedures of item construction in psychology and we want to repeat our most important insights here:

We have repeatedly noticed that the choice of an optimal response format may not be as clear-cut as previously suggested [e.g., @leeSearchOptimalNumber2014]. 
In the current study, we found that items with only two response categories were not unfavorable, as sometimes suggested in the literature. 
While our binary scales obtained lower reliability estimates as expected [see @prestonOptimalNumberResponse2000; @revillaChoosingNumberCategories2014], we did not find clear differences regarding validity and model fit. 
The reliability estimate of the questionnaire informs us only about the precision of measurement and not whether our measurement is valid.
This does not necessarily contradict attempts to choose items based on reliability [e.g., see @zijlmansItemScoreReliabilitySelection2019] since items must have high loadings to achieve high reliability estimates for the scale.
Because reliability is easier to control for by adding more suitable items, construct validity seems to be the stronger argument when choosing the number of response categories.
We believe that decisions on response formats should be empirically founded, especially in high stakes situations (e.g., clinical diagnosis or personnel selection), comparing alternative numbers of response categories in pilot testing. In this context, it is important to recognize that the number of response categories can influence what latent variables are measured [see @hilbertInfluenceResponseFormat2016; @hilbertWhatMeasureEmpirical2022]. Thus, comparing the construct validity of questionnaires differing in the number of response categories is essential.
Nevertheless, it remains necessary to subject response scales to intensive cognitive pretesting to determine a suitable number of categories that work well with participants' actual cognitive processes while answering our questionnaire items [e.g. @tourangeauPsychologySurvey2000].
First, cognitive interviews are necessary to ensure that participants from the target group understand the wording and intended meaning of all items as well as the labels of the response categories.
Second, cognitive interviews can reveal when single categories are systematically overlooked by respondents lacking information or cognitive capacity to differentiate categories. Third, cognitive pretests help assess participants' cognitive load, which should always be kept in mind. For example, two-point scales, which are commonly criticized, have previously been shown to require less effort from the respondents [@hilbertInfluenceResponseFormat2016]. 

We should be aware, that general model fit does not prove how well items are formulated or reveal whether the applied items are helpful to measure the latent variable.
Even when applying best-practices to construct items, it is not guaranteed that model fit will be superior to scales in which items where purposely constructed against such rules [see @pargentCanMakeIt2019; @goretzkoNotVeryPowerful2020].
In the current study, the a-priori most suitable gold-standard items did not always have the highest loading.
Thus, simply selecting items according to their loadings and letting the factor analysis decide which item is good or not is probably insufficient. There should always be a fit between item loading and item content.

We advocate to strongly consider content validity when developing items.
Using gold-standard items for which we would theoretically expect a high factor loading are only a special case of a more general strategy to postulate hypotheses about the function of individual items in a newly constructed scale. Specific hypotheses about the ranking of loadings or the ranking of correlations with construct-divergent items that (in)validate the items intended to measure a latent variable should play a major part in the construction and validation process of each psychological scale. 



<!-- Revisiting the example of *interpersonal warmth* as a personality facet, such additional validation items could, for example, measure warmth itself. TODO -->
<!-- An openness scale or marker items that show high correlations with these warmth items should not be included in the final scale but only used for validation purposes. -->
<!-- These demands are not entirely new but should be newly emphasized based on the results of our analyses, calling for more stringent item construction approaches. -->

<!-- ## Gold-Standard Items for Physical Traits -->

<!-- Gold-standard items did not work as theoretically expected in this study. However, we still believe they are important. Only the gold-standard item for body height – for six, not for two response categories – had the highest loading (point estimate) on the latent variable. @bortolottiRelevanceAdvantagesUsing2013, who previously applied the same procedure with two response categories to investigate a gold-standard item for body height, found a correlation of .86 with body height. This correlation pretty much matches our correlation with the latent variable. The correlation was slightly higher for our 2-response category scale (`r results$load_df_nomod |> filter(rhs == "Koerpergroesse_realW" & categories == 2) |> pull(est.std) |> printnum(gt1 = FALSE)`) compared to our 6-response category scale (`r results$load_df_nomod |> filter(rhs == "Koerpergroesse_realW" & categories == 6) |> pull(est.std) |> printnum(gt1 = FALSE)`), but there were also items which had descriptively equal or higher correlations (biserial correlations) with the sum score than the self-reported physical item (Pearson correlation). This might be because we reported a latent correlation corrected for disattenuation TODO, and our scale had 12 instead of 27 items. Nevertheless, our results depict a conceptual replication of @bortolottiRelevanceAdvantagesUsing2013 with a different questionnaire. -->

<!-- The results differed for the other latent variables of body weight and age, which exhibited lower correlations between the latent variable and their gold-standard items. This seems problematic as these items were designed to be the "gold" measure of the latent variable and should ensure a consistent interpretation. Thus, we should carefully reflect what this finding means for item construction for psychological scales of non-physical traits. If this basic requirement is not met, even for traits that seem rather straightforward to measure, what about more complex constructs? To avoid a misleading interpretation of a latent variable, it might be very helpful to formulate a priori hypotheses about the importance of the constructed items as we did here to test the construct validity of a test. If we, for example, want to measure *interpersonal warmth* as a big five facet and construct items that describe this facet, an item that most directly measures warmth should have its highest loading on the latent variable, otherwise the interpretation of the latent variable is not justified. -->

<!-- If the item "warmth" as gold-standard item perfectly capture the latent trait, why not using it? @allenSingleItem2022 discussed this in more detail. The utility and efficiency of single item measures seem to be an advantage of using a single-item measures, especially the administration, costs and the higher motivation of participants filling out the questionnaires. The authors state that single-item measures are acceptable when constructs are unidimensional, clearly defined, and narrow in scope. The authors argue that against single-item measures can be said that the reliability is at least unknown and that a single item-measure cannot capture the content of a complex construct. Thus, even if we have gold-standard items, we should not easily omit multi-item measures. The main purpose of many questionnaires is measuring the value of a person of a given construct. Thus, the instrument should differentiate between persons (more than five response categories) and should have reliability as high as possible. In many cases this can achieved best using questionnaires with multi-item measures. -->

<!-- It could be argued that a subsample of our used 12-item set might lead to different conclusions and empirical results. This result could occur. But this is a feature not a bug using gold-standard items. The solution with the best interpretability regarding content validity should be considered. We argue that even such a selection process would benefit using gold-standard items. The change of the loading patterns can help to see if a solution leads to a considerable change of the gold-standard-item factor loading. -->

<!-- This approach has the following limitation. In practice, we are used to interpret point estimates of factor loadings. According to @hirschfeldSelecting2014, almost all sample sizes are too small to obtain stable factor loadings or beyond that to interpret differences in factor loadings. Thus, large sample sizes and the consideration of confidence intervals are needed. How large is large enough? This cannot be easily answered, since @wolfSampleSize2013 have shown it is dependent of many parameters e.g., model complexity, number of items, missingness. Another limitation and explanation and for lower loadings of the items constructed compared to the physical items is, that some items have low item difficulties and therefore a restricted variance. During the item construction phase items with somehow extreme formulation worked best to assess height, weight or age (e.g. "I have already lived most of my life"). TODO -->

<!-- We must be aware, that general model fit does not prove how well items are formulated [see @pargentCanMakeIt2019]. Model fit also does not reveal if the applied items are helpful to measure the latent variable. Model fit simply compares a model implied variance/covariance matrix with an empirical variance/covariance matrix. In this study, the a priori most suitable items did not have always the highest discrimination parameters or loadings. Thus, simply selecting items according to their loadings and letting the factor analysis decide which item is good or not is probably insufficient. There must be an item content loading fit. -->

<!-- The reliability estimate of the questionnaire informs us only about the precision of measurement and not whether our measurement is valid. This does not necessarily contradict attempts to choose items based on reliability [e.g., see @zijlmansItemScoreReliabilitySelection2019] since items must have high loadings to achieve high reliability estimates for the scale. -->

<!-- Thus, we suggest using gold-standard items as described above. It should be noted, however, that it is critical not to implement the gold-standard item in the final scale since we would then create a part-whole relationship. This no desirable situation since all test models (classical and IRT models) assume that the probability of a positive response of a person to an item should not depend on this person’s response to any other item [@debelakTestingLocalIndependence2020]. TODO -->

<!-- ## Physical Traits as Psychological Variables -->

<!-- Previous hints suggest that measuring physical attributes through psychological questionnaires is not always connected to a psychological latent variable guiding behavior [@hilbertWhatMeasureEmpirical2022; @vanderlindenUnidimensionalLogisticResponse2016]. Similarly, in our study, it remained unclear if a psychological latent variable beyond body height and weight was measured and how such a latent variable could be interpreted. Only for age there was a latent variable, which can be interpreted as cognitive or psychological age [@barakCognitiveAgeNonchronological1981]. Furthermore, it seems helpful to include additional items, that are not intended to be measured but may further explain the item responses of interest, such as gender or items from the nomological net to reveal possible dependencies and to decide whether these dependencies are in line with the definition of the latent variables. TODO -->


<!-- ## Number of Categories -->

<!-- As expected, reliability estimates were higher for scales with six response categories compared to two categories [@prestonOptimalNumberResponse2000]. The results with regard to model fit and validity, indicated as correlations between latent variables compared to the correlation between gold-standard items, are mixed. Some fit indices suggested slightly better fit for items with two response categories and some for six categories. The same holds true for the differences between the correlations of the gold-standard items and the correlations of the latent variables. Except for reliability, the study revealed no clear picture to choose between two or six response categories. Hilbert et al. [-@hilbertInfluenceResponseFormat2016; -@hilbertWhatMeasureEmpirical2022] showed that the same items with a different number of response categories do not measure the same latent variable.  -->

<!-- Thus, the selection of the response format can change validity. We used 6 response categories since the literature advises to use no middle category. The dichotomous response format was chosen since it is extensively used assessing symptoms. It must be noted that using a 5-point response format different results might have occurred. Another restriction is, that we have used only labels for the extreme responses. Labeling all response categories could change results since this leads to less response biases. These results and limitations highlight that the choice of the number of response categories constructing a questionnaire should be carefully considered. An intensive cognitive pretesting phase can help to understand how people use and understand the categories. Empirical studies can help to choose number of response categories with provides better validity or/and reliability or/and factor structures. -->

<!-- This result highlights that the choice of the number of response categories constructing a questionnaire should be based on an empirical study comparing several options accompanied by an intensive cognitive pretesting phase and not only based on the literature which focuses on maximal reliability.  -->

<!-- ## General Lessons and Recommendations -->

<!-- Gold-standard items might help to ensure the interpretation of the latent variable. The choice of the response format should be based on empirical testing and extensive cognitive interviews. It seems not sufficient to take advice from the literature on how to choose the number of response categories to optimize reliability. The benefit of gold-standard items will be discussed in the following sections. -->

<!-- The results presented here should prompt reflection and reconsideration of standard procedures of item construction in psychology. First, it may be helpful to more strongly consider content validity when developing items. Items that either represent a kind of gold-standard with specific hypotheses about the ranking of the loadings or construct-divergent items that (in)validate the items intended to measure a latent variable should be included in the construction process. Revisiting the example of *interpersonal warmth* as a personality facet, such additional validation items could, for example, measure warmth itself. -->
<!-- An openness scale or marker items that show high correlations with these warmth items should not be included in the final scale but only used for validation purposes. -->
<!-- These demands are not entirely new but should be newly emphasized based on the results of our analyses, calling for more stringent item construction approaches. Second, the choice of an optimal response scale may not be as clear-cut as previously suggested [e.g., @leeSearchOptimalNumber2014]. We found that items with two response categories were not per se unfavorable, as often suggested in the literature. While our binary scales obtained lower reliability estimates as expected [see @prestonOptimalNumberResponse2000; @revillaChoosingNumberCategories2014], other results regarding validity and model fit were mixed. Since reliability is easier to control for by adding more suitable items, construct validity seems to be the stronger argument when choosing the number of response categories. In sum, we believe that decisions on response scales should be empirically founded, especially in high stakes situations (e.g., clinical diagnosis or personnel selection), comparing alternative numbers of response categories in pilot testing. In this context, it is important to recognize that the number of response categories can influence what latent variables are measured [see @hilbertInfluenceResponseFormat2016; @hilbertWhatMeasureEmpirical2022]. Thus, comparing the construct validity of questionnaires differing in the number of response categories is essential. Nevertheless, it remains necessary to subject response scales to intensive cognitive pretesting to determine a suitable number of categories. On the one hand, cognitive interviews can reveal when single categories are systematically overlooked by respondents lacking information or cognitive capacity to differentiate categories. On the other hand, cognitive pretests help assess participants' cognitive load, which should always be kept in mind. For example, two-point scales, which are commonly criticized, have previously been shown to require less effort from the respondents [@hilbertInfluenceResponseFormat2016].  -->

<!-- ### Benefits and Caveats of Gold-standard Items -->

<!-- Based on the results of the present study, we advocate the inclusion of gold-standard items, i.e. items that are supposed to measure the intended construct most directly, to check the interpretation of latent variables in the construction of psychological questionnaires. -->

<!-- **Benefits:** -->

<!-- - Gold-standard items can be implemented very easily without extensive costs and time requirements -->
<!-- - Gold-standard items aid to process to name a latent variable.  -->
<!-- - Gold-standard items can help to develop single-item measures.  -->

<!-- **Caveats:** -->

<!-- -	The loadings of the gold-standard items may change depending on the item subgroup used. This, in turn, can help to clarify the measurement objective or can represent an alternative option for item selection. Present the item set. A solution in which the gold standard item has a comparable loading to other marker items on the latent variable can be easily interpreted in terms of the construct definition and may be preferred over other item sets.  -->
<!-- -	The sample sizes should be large enough [see @wolfSampleSize2013; @hirschfeldSelecting2014] to obtain stable estimates of loadings and confidence intervals should be used to make inferences about the loading of the gold standard variable compared to other variables. A rule of thumb could be that only non-overlapping confidence intervals could be evidence paying attention to the interpretation. -->


<!-- In addition, for questionnaires that are used to make particularly important decisions, we recommend empirically testing the choice of response format, considering validity and/or reliability as well as factor structures to make a well-founded decision. -->
<!-- The pre-selection of response formats (2, 3, 4, 5, 6, 7 response categories or visual analogue scales) should include cognitive pretests of the items since most of the cognitive models [e.g. @tourangeauPsychologySurvey2000] TODO see this as the last part of a four-stage process of the answering process of questionnaires. Cognitive pretests help to see if the response categories are completely used and the labeling of the response categories are well understood by the target group. -->

\

# References

::: {#refs}
:::

# CFA models with correlated errors {#apx-1}

```{r}
r_H10_H11_6 <- results_secondary$cor_errors |>
  filter(lhs == "KGr_22" & rhs == "KGr_23" & categories == 6) |>
  pull(est.std)
r_H10_H11_2 <- results_secondary$cor_errors |>
  filter(lhs == "KGr_22" & rhs == "KGr_23" & categories == 2) |>
  pull(est.std)

r_H4_H9_6 <- results_secondary$cor_errors |>
  filter(lhs == "KGr_16" & rhs == "KGr_21" & categories == 6) |>
  pull(est.std)
r_H4_H9_2 <- results_secondary$cor_errors |>
  filter(lhs == "KGr_16" & rhs == "KGr_21" & categories == 2) |>
  pull(est.std)

r_W6_W12_6 <- results_secondary$cor_errors |>
  filter(lhs == "KGe_30" & rhs == "KGe_36" & categories == 6) |>
  pull(est.std)
r_W6_W12_2 <- results_secondary$cor_errors |>
  filter(lhs == "KGe_30" & rhs == "KGe_36" & categories == 2) |>
  pull(est.std)

r_W3_W7_6 <- results_secondary$cor_errors |>
  filter(lhs == "KGe_27" & rhs == "KGe_31" & categories == 6) |>
  pull(est.std)
r_W3_W7_2 <- results_secondary$cor_errors |>
  filter(lhs == "KGe_27" & rhs == "KGe_31" & categories == 2) |>
  pull(est.std)

r_A3_A9_6 <- results_secondary$cor_errors |>
  filter(lhs == "A_3" & rhs == "A_9" & categories == 6) |>
  pull(est.std)
r_A3_A9_2 <- results_secondary$cor_errors |>
  filter(lhs == "A_3" & rhs == "A_9" & categories == 2) |>
  pull(est.std)

r_A2_A5_6 <- results_secondary$cor_errors |>
  filter(lhs == "A_2" & rhs == "A_5" & categories == 6) |>
  pull(est.std)
r_A2_A5_2 <- results_secondary$cor_errors |>
  filter(lhs == "A_2" & rhs == "A_5" & categories == 2) |>
  pull(est.std)

r_A7_A10_6 <- results_secondary$cor_errors |>
  filter(lhs == "A_7" & rhs == "A_10" & categories == 6) |>
  pull(est.std)
r_A7_A10_2 <- results_secondary$cor_errors |>
  filter(lhs == "A_7" & rhs == "A_10" & categories == 2) |>
  pull(est.std)
```


```{r}
#| label: "tbl-5"
#| tbl-cap: Latent variable loadings for two and six response categories with correlated errors
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: !expr "paste0('CFI = Comparative Fit Index (scaled). ','RMSEA = Root Mean Squared Error of Approximation (scaled). ','SRMR = Standardized Root Mean Residual. ','Scaled chi-square, scaled $df$ (degrees of freedom), and scaled $p$ values are reported. ','Correlations with the latent variable higher as the self-reported physical item are printed in bold. The standardized item loadings for the self-reported physical items are presented in a grey shaded box together with 95% confidence intervals.','The following correlated errors were specified according to high modification indices and good interpretability (parenthesis error correlations for two and six response categories): ','\"I have to look up when I talk to other people.\" (H10) and \"I have to stand at the front of group photos so that I can be seen clearly.\" (H11) (',printnum(r_H10_H11_2),', ',printnum(r_H10_H11_6),'); ','\"In the supermarket, I can reach the things on the top shelf without any problems.\" (H4) and \"I need a chair if I want to get things from the top shelf.\" (H9) (',printnum(r_H4_H9_2),', ',printnum(r_H4_H9_6),'); ','\"I need to lose weight.\" (W6) and \"I should eat less.\" (W12) (',printnum(r_W6_W12_2),', ',printnum(r_W6_W12_6),'); ','\"I have a wide waistband when it comes to pants.\" (W3) and \"My pants have a small waistband.\" (W7) (',printnum(r_W3_W7_2),', ',printnum(r_W3_W7_6),'); ','\"Over time, my mental capacity has decreased.\" (A3) and \"I have years of work experience.\" (A9) (',printnum(r_A3_A9_2),', ',printnum(r_A3_A9_6),'); ','\"Over time, my mental capacity has decreased.\" (A2) and \"Over time, my memory has deteriorated.\" (A5) (',printnum(r_A2_A5_2),', ',printnum(r_A2_A5_6),'); ','\"I have already lived most of my life.\" (A7) and \"My whole life still lies ahead of me.\" (A10) (',printnum(r_A7_A10_2),', ',printnum(r_A7_A10_6),').')"

results_secondary$table5
```

# Item translations {#apx-2}

**Table B2**

Translated items used in this study

| Item          | Item wording (Original wording in German) |
|:--------------|:------------------------------------------|
| **Height 1**  | I keep my head down when I walk through doors. (Ich ziehe den Kopf ein wenn ich durch Türen gehe.) |
| **Height 2**  | In the middle of a crowd, I can see over most other people. (Inmitten einer Menschenmenge kann ich über die meisten anderen Menschen hinwegblicken.) |
| **Height 3**  | Chairs and tables are usually too low for me. (Stühle und Tische sind meistens zu niedrig für mich.) |
| **Height 4**  | In the supermarket, I can reach the things on the top shelf without any problems. (Im Supermarkt komme ich ohne Probleme an die Sachen im obersten Regal.) |
| **Height 5**  | When I drive a car that was previously driven by someone else, I usually have to push the seat backwards. (Wenn ich ein Auto fahre, das vorher jemand anderes gefahren hat, muss ich üblicherweise den Sitz nach hinten schieben.) |
| **Height 6**  | When I stretch out straight in hotel beds, my feet overlap. (Wenn ich mich in Hotelbetten gerade ausstrecke, dann stehen meine Füße über.) |
| **Height 7**  | On airplanes, I bump my knees against the seat in front of me. (Im Flugzeug stoße ich mit den Knien am Vordersitz an.) |
| **Height 8**  | Pants are often too short for me. (Hosen sind mir häufig zu kurz.) |
| **Height 9**  | I need a chair if I want to get things from the top shelf. (Ich brauche einen Stuhl, wenn ich Sachen aus dem obersten Regal holen möchte.) |
| **Height 10** | I have to look up when I talk to other people. (Wenn ich mich mit anderen Menschen unterhalte muss ich nach oben schauen.)  |
| **Height 11** | I have to stand at the front of group photos so that I can be seen clearly. (Ich muss mich bei Gruppenfotos nach vorne stellen, damit ich gut zu sehen bin.) |
| **Height 12** | When I hug other people in greeting, I have to bend downwards. (Wenn ich andere Menschen zur Begrüßung umarme, muss ich mich nach unten beugen.) |
| **Weight 1**  | I am often afraid that chairs will give way under me. (Ich habe oft Angst, dass Stühle unter mir nachgeben.) |
| **Weight 2**  | Other people may think that I sit on the sofa in the evening and eat chocolate and potato chips. (Möglicherweise denken andere Menschen von mir, dass ich abends auf dem Sofa sitze und Schokolade und Chips esse.) |
| **Weight 3**  | I have a wide waistband when it comes to pants. (Bei Hosen habe ich eine große Bundweite.) |
| **Weight 4**  | I am obese. (Ich bin dick.) |
| **Weight 5**  | I weigh a lot. (Ich wiege viel.) |
| **Weight 6**  | I need to lose weight. (Ich müsste abnehmen.) |
| **Weight 7**  | My pants have a small waistband. (Meine Hosen haben eine kleine Bundweite.) |
| **Weight 8**  | I am good at squeezing through narrow gaps. (Ich kann mich gut durch enge Spalten quetschen.) |
| **Weight 9**  | I have a lot of space between the armrests in airplane seats. (Zwischen den Armlehnen in Flugzeugsitzen habe ich viel Platz.) |
| **Weight 10** | I take up a lot of space in the elevator. (Im Aufzug nehme ich viel Platz ein.) |
| **Weight 11** | If I have the choice between the elevator and the stairs, I take the elevator. (Wenn ich die Wahl habe zwischen Aufzug und Treppe, dann nehme ich den Aufzug.) |
| **Weight 12** | I should eat less. (Ich sollte weniger essen.) |
| **Age 1**  | I have physical ailments. (Ich habe körperliche Gebrechen.)  |
| **Age 2**  | Over time, my mental capacity has decreased. (Im Laufe der Zeit hat meine geistige Leistungsfähigkeit abgenommen.) |
| **Age 3**  | I have a lot of life experience. (Ich habe viel Lebenserfahrung.) |
| **Age 4**  | Over time, my ability to react has decreased. (Im Laufe der Zeit hat meine Reaktionsfähigkeit abgenommen.) |
| **Age 5**  | Over time, my memory has deteriorated. (Im Laufe der Zeit hat meine Merkfähigkeit abgenommen.) |
| **Age 6**  | I worry a lot about getting older. (Ich mache mir viele Gedanken über das Älterwerden.) |
| **Age 7**  | I have already lived most of my life. (Den größten Teil meines Lebens habe ich bereits gelebt.) |
| **Age 8**  | I find it increasingly difficult to follow technical developments. (Ich habe zunehmend Schwierigkeiten technischen Weiterentwicklungen zu folgen.) |
| **Age 9**  | I have years of work experience. (Ich habe jahrelange Berufserfahrung.) |
| **Age 10** | My whole life still lies ahead of me. (Mein ganzes Leben liegt noch vor mir.) |
| **Age 11** | I used to be more willing to take risks. (Früher war ich risikofreudiger.) |
| **Age 12** | I carry out everyday activities more slowly than before. (Ich verrichte Alltagstätigkeiten langsamer als früher.) |

*Note:* Original wording in German shown in parenthesis.

# Software versions {#apx-3}

Quarto [@allaireQuarto2025] version {{< version >}} and the extension apaquarto [@schneiderApaquarto2025] were used together with RStudio [@positRstudio2025] to build the manuscript and the manuscript website.  
`r papaja::cite_r(file = "r-references.bib")` were used for data analysis.  
Some dependencies are not included in this list but can be found in the `renv.lock` file in our online repository.
